Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-05-10 Moltres.tex
moved fuel source term def and rephrased interpolation explanation.

in the fuel and by:

@@

in the moderator. $Q_f$ is defined by:

and $Q_g$ is equal to $\gamma Q_f$, representing heat dissipation by gamma and
neutron irradiation in the moderator.

Group constants are generated with either Serpent \cite{leppanen_serpent_2015} 
or Scale \cite{dehart_reactor_2011}. Temperature vs group constant 
interpolation tables are constructed separately for fuel and moderator regions.

>>>>

in the fuel, where the source term $Q_f$ is defined by:

In the moderator, the governing equation for temperature is given by:

@@

in the moderator.

and $Q_g$ is equal to $\gamma Q_f$, where $\gamma$ is a factor representing 
heat dissipation by gamma and neutron irradiation in the moderator.

Group constants are generated with either Serpent \cite{leppanen_serpent_2015} 
or Scale \cite{dehart_reactor_2011} by the modeler. Group constant temperature 
dependence is implmented via interpolation tables, which must be constructed 
separately for fuel and moderator regions.
